`treats` verbose example

### 2023-04-28 inst/gitbook/verbose_example.Rmd
Update verbose_example.Rmd

```{r}
libary(treats)
my_params <- make.bd.params(speciation = rnorm)
my_stop_rule <- list(max.taxa = 50)
trait <- make.traits(process = BM.process, n = 10)
simulation <- treats(bd.params = my_params, stop.rule = my_stop_rule, trait = trait)

>>>>

```{r}
library(treats)
my_params <- make.bd.params(speciation = rnorm)
my_stop_rule <- list(max.taxa = 50)
trait <- make.traits(process = BM.process, n = 10)
simulation <- treats(bd.params = my_params, stop.rule = my_stop_rule, trait = trait)
